\documentclass{article}
\usepackage[utf8]{inputenc}

\title{The Irrationality of $\sqrt{2}$}
\author{Benny Chen}
\date{September 2, 2022}

\usepackage{color}
\usepackage{amsthm}
\usepackage{amssymb} 
\usepackage{amsmath}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{listings}
\usepackage[hidelinks]{hyperref}

\newtheorem{Definition}{Definition}
\newtheorem{Theorem}{Theorem}
\begin{document}

\maketitle

\section{Introduction}
In this short paper we will show that $\sqrt{2}$ is an irrational number. 
In \hyperref[sec:Preliminaries]{Section 2}, we 
will introduce the concepts of rational and irrational numbers. In Section 3, 
we will provide a proof of the fact that $\sqrt{2}$ is irrational. Finally, in 
Section 4, we will discuss what we know about other numbers that are known to be irrational.

\section{Preliminaries}
\label{sec:Preliminaries}
First, we define the rational numbers.
\begin{Definition}
Let $\mathbb{Q}$ be all rational numbers. A rational number is any real number that can be written as a 
ratio such as a quotient or a fraction of two integers.

\end{Definition}
And now we can define the cocept of irrationality.

\begin{Definition}
A rational number is any real number that is not a quotient or a fraction of two integers. The number
would be infinitely continuous decimal without repeating numbers.
\end{Definition}

\section{The Proof}
We are finally ready to show our main result
\begin{Theorem}
    The real number $\sqrt{2}$ is irrational\\
    Proof. 
    Assume that $\alpha = \sqrt{2}$ and $\alpha^{2} = 2$. Now suppose that $\alpha = \frac{m}{n}$ where
    $m, n \in \mathbb{Z}$ and are in their lowest terms. Since $m$ and $n$ are in their lowest terms,
    one or both of $m$ and $n$ must be odd. We can now rearrange $(\frac{m}{n})^2 = 2$ so that $m$ can 
    take the form of an even integer, $a = 2k$. The same logic can be applied for $n$ so it must be even. Since we 
    have shown that $m$ and $n$ are both even, $\frac{m}{n}$ is not in its lowest terms. This is a
    contradiction to our assumption and therefore $\alpha$ must be irrational.
\end{Theorem}
 

\section{Irrational Number}
There are many example of numbers that deviate from being rational, making them irrational.
More famous examples are $\pi$ and Euler's Number. 
\\\\ A good example of a number is $\pi$. It is one of the most famous and well known numbers of all time. $\pi$ is the ratio of 
the circumference of any circle to the diameter of that circle. $\pi$ was first realized by
Greek mathematician Archimedes of Syracuse around 250 B.C who created a algorithm to approximate
the number called Archimedes' constant. The number approximated by Archimedes, $\pi$, is also 
irrational as the decimal continuously goes to infinity. There have been many proofs done on the subject
that show that $\pi$ is irrational from Lambert's proof to Hermite's proof.
\\\\Euler's Number is also a famous irrational number. Euler's number is a important mathematical constant
that is the base of the natural logarithm. Euler's number was first discovered by Jacob Bernoulli in the late 1600's
but was not known until the 17th century which when it was named after Swiss mathematician Leonhard Euler.
Euler's number is similar to $\pi$ in that it is irrational and has a continuous decimal expansion. There have been many proofs
done that support that it is irrational like Euler's proof and Fourier's proof.

\begin{thebibliography}{9}
    \bibitem{website:https://www.britannica.com/science/pi-mathematics}
    Britannica, The Editors of Encyclopaedia. "pi". Encyclopedia Britannica, 14 Mar. 2022, https://www.britannica.com/science/pi-mathematics. 
    
    \bibitem{website:https://mathshistory.st-andrews.ac.uk/HistTopics/e/}
    https://mathshistory.st-andrews.ac.uk/HistTopics/e/
\end{thebibliography}

\end{document}